Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-04 paper/main.tex
restructure discussion & suppl. material

\begin{itemize}
    \item adopt some phrasing from the Speech-Anno-Paper
    \item there is no "cue about" in the English language? Alternatives are
        "give a hint on/about", "indicate"; changed the sentences but should
        ask Alex
\end{itemize}

@@

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that category \texttt{vse\_new} on average comprised the most movie
frames depicting a landscape or the geometry of a setting, and the category
\texttt{vpe\_old} the most frames depicting persons, faces, or
objects.\todo{maybe speak of ratio}
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get a sufficient amount of events per stimulus
segment.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already indicate a change of settings.
\todo[inline]{paragraph above could state that ``fahead'', just N=83; mostly
    just parts (``ear'', ``nose'') of face, or vague description ``his/her
face''}.
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlate with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to localize the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap..
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
on voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Furtherm, we hypothesized that an exclusively auditory
stimulus could localize the PPA in individual subjects and thus
possibly substitute a classic visual localizer experiment.

\todo[inline]{part regarding Sengupta is shortened; they used $t$-maps???}
% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by titrating [?] the $t$-threshold in the range
of [2, 3] in the thresholded $t$-maps (Z>1.64, p<.05 cluster corrected) of three
different $t$-contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple}
stimulus set cf.  \citep{sengupta2016extension}) until we found an isolated
cluster that matched the expected anatomical location based on literature
\citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we used the same contrast of each
naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see ).
% what it depicts
Each subplot of Figure \ref{fig:bland-altman} visualizes the mean value and
difference (localizer minus AD) of two spatially corresponding voxels in the
unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

% previous studies
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we use here also operationalize spatial
perception via general linear model (GLM) $t$-contrasts in two naturalistic
stimuli.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentially
occurring in an audio-visual movie and its audio-description.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description reveal significant activation in the PPA but
restricted its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in one subjects.
% meaning 1
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning 2
Our results provide further evidence that the PPA can be divided into functional
subregions. An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

\subsection{PPA; AV \& AD; group \& individuals}

@@

\subsubsection{AV: group}

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content
(color, faces, language, and human bodies) of movie frames found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the movie frames' content
(color, faces, language and human bodies), we categorized each frame after a cut
independent of its content. \todo{PPA in \citep{hasson2004intersubject} but do
reverse ISC; Bartels' clusters are actually pretty big too}
% hypo
Despite this ad hoc approach, we hypothesized that [confounding variables
could/would average out and] our whole-brain analyses would lead to significant
clusters in the PPA.
% results
Group results of the AV stimulus' primary contrast yielded a cluster that span
the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
The cluster also extends into medial regions (dorsal precuneus and dorsal
posterior cingulate cortices), and into more posterior regions (occipital
fusiform gyrus and intracalcarine cortex) bilaterally.
% confound of higher perception
The larger extension into more posterior, primary visual areas can be attributed
to the averaging process that did not control for confounding visual features or
the attentional focus of study participants.

\todo[inline]{I am pretty surprised the clusters are not all over the brain.  I
do not know where/how do phrase it but should be mentioned imo}

% shortcomings
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.
% solution
Future studies that aim to use a movie to localize different visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

\todo[inline]{nice that the following is mentioned but what to do with it?
Movies are nice but have idiosyncrasies; so, maybe you should be aware of these
idiosyncrasies (and control for it) in case you wanna use movies for research?}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}).
%
Film directors tend to establish the geometry of locations earlier in the movie
and to later focus more on persons and objects relevant to the evolved plot
later  \citep{brown2012cinematography, mercado2011filmmakers}.

% summary: nevertheless
\todo[inline]{Overall summary for AV: so, yes, what is the main message of this
``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
widespread}

\subsubsection{AD: group}

@@

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA, and only for sentences describing famous places
compared to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed an
whole-brain analysis.
% our results
Group results of audio-description's primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

@@

\subsubsection{AD: shortcoming}

\todo[inline]{at the moment positioned here; makes sense at a couple of other
positions; not sure yet}

@@

\subsubsection{AD: individuals}

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of nouns offered a more precise way to
operationalize the perception of spatial information than the annotation of cuts
and locations, we also hypothesized that analyzing the data from the
audio-description could localize the PPA in individual persons.
%
Hence to test if an auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the results from the audio-description's
primary contrast on an individual level.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
cluster-corrected) in one contrast.
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows only a right-lateralized PPA ROI),
and a unilateral significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
reveal that clusters are spatially restricted to the anterior part of individual
PPAs.
% conclusion
Thus, the increased hemodynamic activity in the anterior part of the PPA
revealed on the group level is not just a by-product of the averaging process
[as it can reliably be found in individual study participants.]
% conclusion
Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Further studies that aim for individual diagnostics / ROI localization should
nevertheless test more than one contrast to gain the ``best'' individual
ROIs.\todo{..ouff}

@@

% question
This raises the question if the different activation patterns can be attributed
to different features inherent in visual compared to verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than the pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent/inherent in both
visual and verbal stimuli.

>>>>

\begin{itemize}
    \item in case the additional contrast stay in supplemental material, just
        speak of contrast not ``primary contrast''
    \item adopt some phrasing from the Speech-Anno-Paper
    \item there is no "cue about" in the English language? Alternatives are
        "give a hint on/about", "indicate"; changed the sentences but should
        ask Alex
\end{itemize}

@@

% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that category \texttt{vse\_new} on average comprised the most movie
frames depicting a landscape or the geometry of a setting, and the category
\texttt{vpe\_old} the most frames depicting persons, faces, or
objects.\todo{maybe speak of ratio}
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get a sufficient amount of events per stimulus segment.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already indicate a change of settings.
\todo[inline]{paragraph above could state that ``fahead'', just N=83; mostly
    just parts (``ear'', ``nose'') of face, or vague description ``his/her
face''}.
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.
%
\todo[inline]{it's probally not about the soundscape anymore (to speculative)
but about the somewhat correlation of nouns and cuts}

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlate with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description to results gained from a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
On the level single subjects, we also assess the performance of the exclusively
auditory naturalistic stimulus as a substitute for a visual paradigm to localize
the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts withn a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen.  on
voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual subjects and thus possibly substitute a classic visual
localizer experiment.

\todo[inline]{part regarding Sengupta is shortened; they used $t$-maps???}
% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registed to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we also operationalized spatial perception via
general linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentially
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description reveal significant activation in the PPA but
restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in one subjects.
% meaning 1
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning 2
Our results provide further evidence that the PPA can be divided into functional
subregions. An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

\subsection{PPA group}

@@

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content
(color, faces, language, and human bodies) of movie frames found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the movie frames' content
(color, faces, language and human bodies), we categorized each frame after a cut
independent of its content. \todo{Bartels' clusters are actually pretty big too}
% hypo
Despite this ad hoc approach, we hypothesized that [confounding variables
could/would average out and] our whole-brain analyses would lead to significant
clusters in the PPA.
% results
Group results of the AV stimulus' primary contrast yielded a cluster that span
the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
The cluster also extends into medial regions (dorsal precuneus and dorsal
posterior cingulate cortices), and into more posterior regions (occipital
fusiform gyrus and intracalcarine cortex) bilaterally.
% confound of higher perception
The larger extension into more posterior, primary visual areas can be attributed
to the averaging process that did not control for confounding visual features or
the attentional focus of study participants.
%
\todo[inline]{I am pretty surprised the clusters are not all over the brain.  I
do not know where/how do phrase it but should be mentioned imo}
% solution
Future studies that aim to use a movie to localize visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}).
% establishing shots vs. e.g. over-the-shoulder shots
Film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved
\citep{brown2012cinematography, mercado2011filmmakers}.
%
\todo[inline]{nice that exploited confound structure is mentioned but what to do
with it? hey, look, it works? movies are nice but have idiosyncrasies? so, maybe
you should be aware of these idiosyncrasies (and control for it) in case you
wanna use movies for research?}

% summary: nevertheless
\todo[inline]{Overall summary for AV \& concluding statement!?!}

\todo[inline]{so, yes, what is the main message of this
``cross-modal-control-movie-thing''??}

@@

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA, and only for sentences describing famous places
compared to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed a
whole-brain analysis.
% our results
Group results of audio-description's primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

@@

% AD shortcomings

@@

\subsection{PPA individuals (AD)}

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of nouns offered a more precise way to
operationalize the perception of spatial information than the annotation of cuts
and locations, we also hypothesized that analyzing the data from the
audio-description could localize the PPA in individual persons.
%
Hence to test if an auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the results from the audio-description's
primary contrast on an individual level.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
cluster-corrected) in one contrast.
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows only a right-lateralized PPA ROI),
and a unilateral significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size is not just a by-product of the averaging
process but the same pattern can can reliably be found in individual study
participants.
% question
This raises the question if the different activation patterns can be attributed
to different features inherent in visual compared to verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than the pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent/inherent in both
visual and verbal stimuli.

% conclusion
Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Further studies that aim for individual diagnostics / ROI localization should
nevertheless test more than one contrast to gain the ``best'' individual
ROIs.\todo{..ouff}

@@

\subsection{RSC \& LOC = non random clusters => naturalistic stimuli are
cool}

% no random clusers
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC are known to be scene-selective regions (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% conclusion
\todo[inline]{concluding statement}

\section{conlusion}

\todo[inline]{scientific data has no conclusion -> last paragraph}
